The pollination trade-off

### 2019-04-08 paper/manuscript.Rmd
Improve manuscript readability - more margin, larger font

---
title: "The pollination trade-off"
author: "E. Fernando Cagua^1^, Hugo J. Marrero^2^, Jason M. Tylianakis^1^, Daniel B. Stouffer^1^"
bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
---

>>>>

---
title: "The pollination trade-off"
author: "E. Fernando Cagua^1^, Hugo J. Marrero^2^, Jason M. Tylianakis^1^, Daniel B. Stouffer^1^"
bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
---
